---
title: "Regression Models"
author: "Janus"
date: "Friday, November 16, 2015"
output: html_document
---
Context

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

"Is an automatic or manual transmission better for MPG"
"Quantify the MPG difference between automatic and manual transmissions"

Question

Take the mtcars data set and write up an analysis to answer their question using regression models and exploratory data analyses.

Your report must be:

Written as a PDF printout of a compiled (using knitr) R markdown document.
Brief. Roughly the equivalent of 2 pages or less for the main text. Supporting figures in an appendix can be included up to 5 total pages including the 2 for the main report. The appendix can only include figures.
Include a first paragraph executive summary.
Upload your PDF by clicking the Upload button below the text box.

Peer Grading

The criteria that your classmates will use to evaluate and grade your work are shown below. 
Each criteria is binary: (1 point = criteria met acceptably; 0 points = criteria not met acceptably)
Your Course Project score will be the sum of the points and will count as 40% of your final grade in the course. 


Load Data 
```{r}
data(mtcars)
```

Exploratory analysis
```{r}
#Results omited for not having enought space and not needed.
summary(mtcars)
```

```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am,labels=c('Automatic','Manual'))

#Result shown in the Appendix
summary(mtcars)
```
Regression model
```{r}
full.model <- lm(mpg ~ ., data = mtcars)
best.model <- step(full.model, direction = "backward")
```
```{r}
#Result shown in the Appendix
summary(best.model)

```

```{r}
t.test(mpg ~ am, data = mtcars)
```

```{r}
#Result shown in the Appendix
boxplot(mpg ~ am, data = mtcars, col = "green", ylab = "miles per gallon")
```
*****Conclusion

According to the results, cars with a manual transmission are better for mpg than cars with an automatic transmission. The rate of change of the conditional mean mpg with respect to am is about 1.8, and we are 95% confident that this value varies between -1.06 and 4.68. There are however some limitations to this study. 


Appendix

Exploratory analysis

```{r, echo=FALSE}
summary(mtcars)
```

Regression model
```{r}
summary(best.model)
```

```{r}
boxplot(mpg ~ am, data = mtcars, col = "green", ylab = "miles per gallon")
```
```{r}
par(mfrow=c(2, 2))
plot(best.model)
```

