---
title: "Regression Models"
author: "Janus"
date: "Friday, November 21, 2015"
output: pdf_document
---
Context

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

"Is an automatic or manual transmission better for MPG"
"Quantify the MPG difference between automatic and manual transmissions"

Load Data 
```{r}
data(mtcars)
```

Exploratory analysis
```{r}
#Results omited for not having enought space and not needed.
summary(mtcars)
```

```{r}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am,labels=c('Automatic','Manual'))

#Result shown in the Appendix
summary(mtcars)
```
Regression model
```{r}
full.model <- lm(mpg ~ ., data = mtcars)
best.model <- step(full.model, direction = "backward")
```
```{r}
#Result shown in the Appendix
summary(best.model)

```

```{r}
t.test(mpg ~ am, data = mtcars)
```

```{r}
#Result shown in the Appendix
boxplot(mpg ~ am, data = mtcars, col = "green", ylab = "miles per gallon")
```
Conclusion

According to the results, cars with a manual transmission are better for mpg than cars with an automatic transmission. The rate of change of the conditional mean mpg with respect to am is about 1.8, and we are 95% confident that this value varies between -1.06 and 4.68. There are however some limitations to this study. 


Appendix

Exploratory analysis

```{r, echo=FALSE}
summary(mtcars)
```

Regression model
```{r}
summary(best.model)
```

```{r}
boxplot(mpg ~ am, data = mtcars, col = "green", ylab = "miles per gallon")
```
```{r}
par(mfrow=c(2, 2))
plot(best.model)
```

